A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-21 6_validation.tex
remove old comment
new statistics, new figures, new colors

\begin{figure*}
\centering
\setlength{\figheight}{0.22\textwidth}
\setlength{\figwidth}{0.31\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-computime2.pdf}
%\includegraphics[width=\figwidth]{sources-validation-computime2.pdf}
\caption{Computation time}
\label{computime}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widthHistogram.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{Extrusion widths}
\label{widthHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-indexedwidths2.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{Extrusion width per index}
\label{widthIndexedHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-overunderfill.pdf}
%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
\caption{Over- and underfill}
\label{over_underfill}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-smoothness.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
\caption{Site angles}
\label{smoothness}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-smoothnessNoTransition.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
\caption{Site angles (inward distributed)}
\label{smoothnessNoTransition}
\end{subfigure}

\caption{
Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

@@

\iffalse
\todo{Maybe test the following qualities:}
\begin{itemize}
\item visual consistency of flat top skin surface
\item graphs of tensile tests on thin walled object
\end{itemize}
\fi

>>>>

\begin{figure*}
\centering
\setlength{\figheight}{0.25\textwidth}
\setlength{\figwidth}{0.32\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-over-underfill.pdf}
%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
\caption{\revise{}{Over- and underfill}}
\label{over_underfill}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-print-time.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
\caption{\revise{}{Print time}}
\label{printtime}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-path-counts.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{\revise{}{Path counts}}
\label{pathcounts}
\end{subfigure}

\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widths.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{\revise{}{Extrusion widths}}
\label{widthHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-angles.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
\caption{\revise{}{Site angles}}
\label{smoothness}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-computime2.pdf}
%\includegraphics[width=\figwidth]{sources-validation-computime2.pdf}
\caption{Computation time}
\label{computime}
\end{subfigure}

\caption{
Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
Note the use of a logarithmic scale \revise{}{in the bottom graphs }on the Y-axes and \revise{on some of}{for \subref{computime} on} the X-axes as well.
}
\label{statisticsfig}
\end{figure*}

@@
